Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Reusable spec: fix quotation and tt

RSpec provides an explicit mechanism to facilitate reuse of pieces of
specification~\cite{rspec}.
In Haskell we get reusability for free, it does not require any
explicit support from Hspec.
The following example illustrates this.

\begin{quote}
  TBD: not sure, if this adds anything

This not only shows that functional programming can deliver what OO
has always claimed, but it is also awfully useful.
\end{quote}
Here is a specification that documents that a list is a monoid:

@@

\noindent Doctest provides both, an executable and a library.  The library
exposes a function \verb|doctest| of type:

@@

\noindent Doctest's own `main` is simply:
\begin{quote}
\small
\begin{verbatim}
main = getArgs >>= doctest
\end{verbatim}
\end{quote}

\noindent Consequently, it is possible to create a custom executable
for a project, by passing all command-line arguments that are required
for that project to `doctest`.  A simple example looks like this:

>>>>

RSpec provides an explicit mechanism to facilitate reuse of pieces of
specification~\cite{rspec}.
In Haskell we get reusability for free, it does not require any
explicit support from Hspec.
The following example illustrates this.
Here is a specification that documents that a list is a monoid:

@@

\noindent Doctest provides both, an executable and a library.  The library
exposes a function ``{\tt doctest}'' of type:

@@

\noindent Doctest's own {\tt main} is simply:
\begin{quote}
\small
\begin{verbatim}
main = getArgs >>= doctest
\end{verbatim}
\end{quote}

\noindent Consequently, it is possible to create a custom executable
for a project, by passing all command-line arguments that are required
for that project to {\tt doctest}.  A simple example looks like this:
